---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# VideoGames

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of VideoGames is to provide a streamlined toolkit for exploring and analyzing trends in global video game sales and development. Built for data analysis, it includes a data set along with functions for visualizing and modeling patterns in game performance, genre evolution, regional markets, and much more! 

## Installation

You can install rclimateca from CRAN with:

``` r
install.packages("VideoGames")
```

You can install the development version of VideoGames from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("clinker-smith/VideoGames")
```

If you can load the package, everything worked!

``` r
library(VideoGames)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(VideoGames)
## basic example code
```



## More Information 

See vignette("vg_instructions", package = "VideGames") and ?vg_instructions for more information about using VideoGames.

